What words ought to exist? \\ {\normalsize Coining with coinduction}

### 2013-09-22 wishlist/paper.tex
Typo in paper

% \usepackage{eclbkbox}
\usepackage{amsmath}
\usepackage{amssymb}
% \usepackage{amscd}
% \usepackage{xy}
\usepackage{graphicx}
% \usepackage{fancyhdr}
% \usepackage{color}
% \usepackage[dark,all,bottom,landscape,timestamp]{draftcopy}
% \usepackage{everypage}

@@

\begin{figure}
\includegraphics[width=\linewidth]{wishlist-cdf}
\vspace{-0.1in}\caption{Cumulative distribution of word frequency.
  Approximately 25,000 different words (y axis) were issued 55 times
  or fewer (x axis). The ``total'' area does not appear much larger
  than its components because this is a log-log plot.}
\label{fig:gamedistribution}
\end{figure}

@@

\begin{figure}
\includegraphics[width=\linewidth]{coin1}
\caption{Markov chain for the SOWPODS word list, where darker squares
indicate higher probability. The darkest is the transition from {\it q}
to {\it u} ($98\%$), which is not surprising.}
\label{fig:sowpodsbigrams}
\end{figure}

@@

\begin{figure}
\includegraphics[width=\linewidth]{italiancoin1}
\caption{Markov chain for the Italian language. Again darker cells
  indicate higher probability. Italian has more lexicographic
  structure recognizable from bigraphs than English does: Note that
  the extremely rare letters ``j'', ``k'', ``q'', ``w'', ``x'', and
  ``y'' have almost empty rows. ``z'' very frequently follows ``z'',
  as in {\it pizza}. Words almost always end in a vowel.}
\label{fig:italianbigrams}
\end{figure}

@@

One criticism of this approach is that it considers every word in the
word list to be equally important.\!\footnote{In fact, the common part
  of words with many different conjugations is in essence counted many
  times. This means {\it ornithology} in its six different forms
  contributes six times as much to our model as the word {\it the}!} I
object on the philosophical grounds that some words that already exist
{\em ought to exist more} than other words that already exist. For
example, {\it congenital} is a much nicer word than the plain ugly
{\it congenial}, and is reflected by the fact that {\it congenial} is
used five times more frequently than {\it
  congenial}.\!\footnote{14,200,000 times to 2,820,000, on the
  Internet, according to Google.} In this section, we produce Markov
models of words weighted by the frequency with which people tend to
use them. This is just a simple matter of training the model on some
natural language corpus (with many occurrences of each word, or no
occurrences of unpopular words) rather than a flat list of all alleged
words.

{\bf Facebook.}\ Since the best research is intensely navel-gazing, I started by 
analyzing a corpus of my own writing, specifically my Facebook status
updates since March~2006. There were 1,386 status updates containing
such jems as ``Tom Murphy VII thinks mathfrak is straight ballin''
and ``Tom Murphy VII global L\_50 reused for unused\_36166!!''. The
most likely words with $n=4$:

@@

The solution is to use coinduction. Most people remember induction
from school, maybe, which is the one where you have some base case
like ``0 is even'', and then you prove that all numbers are either
even or odd by assuming ``$n$ is even or odd'' and proving ``$n + 1$
is even or odd''.

most people remember induction, perhaps 
coinduction: never gonna give you up. once you pop you can't stop.

@@

From this we can conclude that 16\% of people wish {\it nurm} were a word, and so on.
These words did not come with definitions, except for {\it gruntle}, which Jessica
gives as ``the opposite of distgruntle''. This is actually already a word, but
it was the inspiration for Section~\ref{sec:backformation}. {\it etsy} is the name
of a popular on-line crafts community so I don't know why Rob would suggest that.
The meaning of {\it wafflucinations} is clear from morphological analysis.

@@

% TODO: backformation, stripping dis- and anti- and un- from words
% then checking to see if they're still words?

@@

@@

sweeeeeeeeeeeeeeeeeeet with 19 {\it e}s, which means ``Really sweet.''

``rane'' sounds too much like ``rain'', but ``sare'' has a unique pronunciation and many people seem to think it's already a word. ``cho'' is similarly easy to pronounce and spell. I propose that it be defined as ``A kind of cheese,'' so that we can really nail the new triple entendre on the classic joke.

In this paper I investigated several different ways of answering the
question: What words ought to exist? Each method produces different
words, and some don't work that well, but nonetheless we have several
rich sources of words, each time scientifically justified.

Nobody really likes writing conclusions, so I will just now summarize
the paper by the giving the most likely sentences that I have not
already written.

% XXXX

% \begin{Verbatim}
facebook wall posts, 4-grams
100 top paths:
0.002525504 pittsburgh
0.002093510 steelers
0.002093510 sfo
0.001953943 it's
0.001256106 bdl
0.001116539 sigbovik
0.001099196 facebook
0.000976971 mic
0.000976971 s
0.000976971 can't
0.000837404 i'm
0.000837404 icfp
0.000837404 app
0.000697837 x
0.000697837 drunj
0.000697837 g
0.000616021 ther
0.000558269 doesn't
0.000558269 's
0.000558269 sr
0.000558269 pm
0.000558269 fyi
0.000558269 wtf
0.000558269 k
0.000558269 don't
0.000558269 today's
0.000558269 m
0.000558269 what's
0.000456766 iphone
0.000429438 inted
0.000418702 oh
0.000418702 phl
0.000418702 gonna
0.000418702 pre
0.000418702 zrh
0.000418702 th
0.000418702 h
0.000418702 b
0.000418702 n
0.000418702 ok
0.000418702 d
0.000418702 that's
0.000418702 rex
0.000418702 fanzibar
0.000418702 st
0.000418702 kinda
0.000418702 didn't
0.000355262 cally
0.000334962 brillobox
0.000314027 superburrito
0.000305304 weath
0.000279135 techno
0.000279135 vii

trigrams, including comments:
100 top paths:
0.003013897 it's
0.001856422 ther
0.001704432 i'm
0.001503910 sfo
0.001102867 -
0.001102867 oh
0.001050350 don't
0.001002607 haha
0.001002607 s
0.000902346 bdl
0.000808769 mic
0.000808769 that's
0.000776981 pittsburgh
0.000705812 thes
0.000701825 ok
0.000645063 can't
0.000601564 icfp
0.000601564 k
0.000583335 didn't
0.000507201 runj
0.000501303 g
0.000501303 omg
0.000501303 x
0.000485262 ins
0.000453126 sout
0.000450580 ands
0.000449950 coff
0.000425932 reat
0.000425133 ning
0.000416189 pittle
0.000412468 getty
0.000407151 ster
0.000401043 sr
0.000401043 pm
0.000401043 m
0.000401043 wtf
0.000401043 aw
0.000401043 d
0.000401043 fyi
0.000401043 ple
0.000401043 's
0.000400791 phon
0.000386315 weat
0.000384116 befor
0.000375978 els
0.000374307 als
0.000357782 nothe
0.000354769 app
0.000354769 appy
0.000354422 they're
0.000353750 wate
0.000345727 there's
0.000340508 res
0.000339344 mes
0.000334202 ove
0.000326473 wher
0.000324373 lity
0.000319011 hotos
0.000316613 dea
0.000315777 sigbovik
0.000315105 ver
0.000314965 thand
0.000310607 outh
0.000300782 n

facebook, n = 2
100 top paths:
0.010628671 ing
0.007144197 th
0.005025442 st
0.004291375 re
0.002932937 ne
0.002662094 se
0.002546194 whe
0.002108786 ther
0.001923496 al
0.001669458 con
0.001652820 wor
0.001498222 ch
0.001495485 wis
0.001379778 i'm
0.001336166 jus
0.001302469 sh
0.001280888 yout
0.001244352 fo
0.001225250 le
0.001224422 pre
0.001221357 ar
0.001201881 com
0.001200574 ge
0.001165417 thes
0.001116295 som
0.001108305 fing
0.001104851 ang
0.001102867 -
0.001102706 it's
0.001039704 ist
0.001036886 hing
0.001007930 ou
0.001002607 s
0.000967282 de
0.000932965 en
0.000926568 tor
0.000827260 wat
0.000827151 oh
0.000814235 cor
0.000812961 ned
0.000783696 lis
0.000762020 ple
0.000760162 whis
0.000759898 sed
0.000755396 res
0.000728412 mor
0.000728049 ong
0.000727818 don
0.000720098 cand
0.000710277 ning
0.000708380 ithe
0.000693547 ame
0.000659248 ty
0.000656211 dow
0.000635771 ha
0.000633225 ext
0.000601564 k
% \end{Verbatim}

>>>>

% \usepackage{eclbkbox}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{code}
% \usepackage{amscd}
% \usepackage{xy}
\usepackage{graphicx}
% \usepackage{fancyhdr}
% \usepackage{color}
% \usepackage[dark,all,bottom,landscape,timestamp]{draftcopy}
% \usepackage{everypage}

% \pagestyle{empty}

@@

\begin{figure}[t]
\includegraphics[width=\linewidth]{wishlist-cdf}
\vspace{-0.1in}\caption{Cumulative distribution of word frequency.
  Approximately 25,000 different words (y axis) were issued 55 times
  or fewer (x axis). The ``total'' area does not appear much larger
  than its components because this is a log-log plot.}
\label{fig:gamedistribution}
\end{figure}

@@

\begin{figure}[t]
\includegraphics[width=\linewidth]{coin1}
\caption{Markov chain for the SOWPODS word list, where darker squares
indicate higher probability. The darkest is the transition from {\it q}
to {\it u} ($98\%$), which is not surprising.}
\label{fig:sowpodsbigrams}
\end{figure}

@@

\begin{figure}[t]
\includegraphics[width=\linewidth]{italiancoin1}
\caption{Markov chain for the Italian language. Again darker cells
  indicate higher probability. Italian has more lexicographic
  structure recognizable from bigraphs than English does: Note that
  the extremely rare letters ``j'', ``k'', ``q'', ``w'', ``x'', and
  ``y'' have almost empty rows. ``z'' very frequently follows ``z'',
  as in {\it pizza}. Words almost always end in a vowel.}
\label{fig:italianbigrams}
\end{figure}

@@

One criticism of this approach is that it considers every word in the
word list to be equally important.\!\footnote{In fact, the common part
  of words with many different conjugations is in essence counted many
  times. This means {\it ornithology} in its six different forms
  contributes six times as much to our model as the word {\it the}!} I
object on the philosophical grounds that some words that already exist
{\em ought to exist more} than other words that already exist. For
example, {\it congenital} is a much nicer word than the plain ugly
{\it congenial}, and is reflected by the fact that {\it congenital} is
used five times more frequently than {\it
  congenial}.\!\footnote{14,200,000 times to 2,820,000, on the
  Internet, according to Google.} In this section, we produce Markov
models of words weighted by the frequency with which people tend to
use them. This is just a simple matter of training the model on some
natural language corpus (with many occurrences of each word, or no
occurrences of unpopular words) rather than a flat list of all alleged
words.

{\bf Facebook.}\ Since the best research is intensely navel-gazing, I started by 
analyzing a corpus of my own writing, specifically my Facebook status
updates since March~2006. There were 1,386 status updates containing
such gems as ``Tom Murphy VII thinks mathfrak is straight ballin''
and ``Tom Murphy VII global L\_50 reused for unused\_36166!!''. The
most likely words with $n=4$:

@@

The solution is to use coinduction. Most people remember induction
from school, maybe, which is the one where you have some base case
like ``0 is even'', and then you prove that all numbers are either
even or odd by assuming ``$n - 1$ is even or odd'' and proving ``$n$
is even or odd''. From this we conclude that every number is either
even or odd. The idea is the proof shows how to, for any given number
$m$, count down to the base case ``0 is even'', and then repeatedly
apply the $n-1$ step (inductive step) to get back up to $m$. This is a
great way to prove facts about finite things like numbers. Think of
induction as a way you prove a statement like ``Good to the last
drop,'' or ``There's always room for Jello.''

Coinduction is a good proof technique for infinite things, like a
sorted infinite list of possible strings. The idea behind coinduction
is kind of like, you prove something like ``0 is a number'' (the base
case), then prove something like ``if $n$ is a number, then $n+1$ is a
larger number'', and then conclude that there exists an infinite
series of numbers, each larger than the previous one. Think of
coinduction as a way you prove a statement like ``Once you pop, you
can't stop,'' or ``Never gonna give you up.''

To sort the infinite list we don't actually use coinduction (we're
not going to prove anything, just implement it), but its computational
counterpart, corecursion. I just can't resist the ``coin'' pun.

What we do is define a function ``most probable paths'', which returns
a (possibly infinite) stream of strings for a given starting state.
Each string is finite and ends with the terminal symbol \>, and they
appear sorted by decreasing probability. (The most probable words
overall will be just the first elements from the stream returned by
this function when using a starting state like \<\<\< for $n=3$.)
Since we don't want to explore all possible strings in order to
produce this list (there are infinitely many), the trick is to put a
lower bound on the probability of the words that will be included.
There are always finitely many words with probability greater than a
given positive value, unless the Markov chain contains a cycle where
each edge has probability 1. (This is impossible for Markov chains
created only by observing finite strings, such as all the ones in this
paper.) It is efficient to use a very small lower bound with this
algorithm, like 0.00000000000001.

So the specification for ``most probable paths'' is to return all of
the strings (that end with \>) that exceed the given lower bound in
probability, sorted in descending probability order. It is easy to
check the path directly to \>; we compare its probability to the lower
bound by just looking it up in the table, and consider it if it
exceeds the lower bound. For any other symbol {\it sym}, we will
proceed (co)recursively: Call the probability of seeing {\it sym} next
{\it p}, and then compute {\it tails}, all of the most probable paths
starting in the state we would be in upon seeing {\it sym}. We turn
{\it tails} into the sorted stream for the current state by just
adding {\it sym} to the beginning of each string in it, and
multiplying the probability by {\it p}. It remains sorted because
multiplying by the same {\it p} is monotonic. The most important
thing, which makes the algorithm practical (indeed terminate at all),
is that we pass in a new lower bound: The current lower bound divided
by {\it p}. After all, the outputs will be multipled by {\it p}, so
they have to exceed this in order to meet the lower bound. This tends
to increase the lower bound (sometimes over 1) since probabilities are
between 0 and 1. This way, we only need to search a few symbols deep
before it's clear that no string can exceed the lower bound.

Now we have a list of sorted streams, at most one for each symbol in
our alphabet. It is fairly straightforward to merge these into a
single sorted stream, by only looking at the first element from each
one. Pseudocode for {\tt most\_probable\_paths} appears in
Figure~\ref{fig:mostprobablepaths} and for {\tt merge\_sorted} in
Figure~\ref{fig:mergesorted}. Performance of this code is great;
building the Markov chains (or even just reading the dictionary files)
dominates the latency of the analyses in this paper.

\begin{figure*}
\begin{code}
fun most\_probable\_paths \{ lower_bound : real, state : state \}
       : \{ string : symbol list, p : real \} stream =
  let
    fun nexts i =
      case symbol\_from\_int i of 
      NONE => nil
    | SOME sym =>
      let 
        val p = (* probability of seeing sym in this state *)
      in
        if p < lower\_bound
        then nexts (i + 1)
        else if sym = end\_symbol
             then S.singleton \{ string = nil, p = p \} :: nexts (i + 1)
             else 
               let
                   val lb' = lower\_bound / p
                   val tails =
                       most\_probable\_paths \{ lower\_bound = lb',
                                             state = advance\_state (state, sym) \}
               in
                   (* Now multiply through the probabilities and add the symbol
                      to the head of the strings. *)
                   Stream.map (fn \{ string = t, p = p' \} =>
                               \{ string = sym :: t, p = p * p' \}) tails ::
                   nexts (i + 1)
               end
      end

    (* Try all next symbols. *)
    val streams = nexts 0
  in
    S.merge\_sorted bysecond\_real\_descending streams
  end
\end{code}
\caption{Pseudocode for {\tt most\_probable\_paths}. {\tt advance\_state}
gives a new state from a previous state and symbol observed, so that
for example {\tt advance\_state(abc, z)} gives {\tt bcz}. The pseudocode
for {\tt merge\_sorted} is given in Figure~\ref{fig:mergesorted}.}
\label{fig:mostprobablepaths}
\end{figure*}

\begin{figure*}[t]
\begin{code}
fun merge\_sorted cmp l =
  let
      fun ms nil () = Nil
        | ms (s :: t) () =
          case force s of
              Nil => ms t ()
            | Cons (v, ss) =>
              ms\_insert v [ss] t

      and ms\_insert bv sg nil =
          Cons (bv, delay (ms sg))
        | ms\_insert bv sg (s :: t) =
          case force s of
              Nil => ms\_insert bv sg t
            | Cons (v, ss) =>
                case cmp (bv, v) of
                    GREATER =>
                      ms\_insert v (singleton bv :: ss :: sg) t
                  | \_ => ms\_insert bv (s :: sg) t
  in
      delay (ms l)
  end
\end{code}
\caption{Pseudocode for {\tt merge\_sorted}. {\tt ms} merges a
sorted list, and {\tt ms\_insert} is a helper where we have a
candidate best value {\tt bv} which will either be the one we
return at the head of the stream, or we'll replace it and then
stick {\tt bv} somewhere to be returned later. (This algorithm
can be improved by making a data structure like a (co)heap;
this is just a simple first pass.)}
\label{fig:mergesorted}
\end{figure*}

@@

From this we can conclude that 16\% of people wish {\it nurm} were a word, and so on.
These words did not come with definitions, except for {\it gruntle}, which Jessica
gives as ``the opposite of disgruntle''. This is actually already a word, but
it was the inspiration for Section~\ref{sec:backformation}. {\it etsy} is the name
of a popular on-line crafts community so I don't know why Rob would suggest that.
The meaning of {\it wafflucinations} is clear from morphological analysis.

@@

@@

In this paper I investigated several different ways of answering the
question: What words ought to exist? Each method produces different
words, and some don't work that well, but nonetheless we have several
rich sources of words, each time scientifically justified. I conclude
with a section of recommendations for words that ought to exist, along
with definitions.

@@

{\it Sweeeeeeeeeeeeeeeeeeet} with 19 {\it e}s is the clear favorite
based on analysis of usage, so this one should be introduced. It means
``Really sweet.''

{\it Rane} sounds too much like {\it rain}, but {\it sare} has a
unique pronunciation and many people seem to think it's already a
word. I propose that {\it sare} be introduced as a noun meaning, ``a
word that sounds real but isn't.''

{\it Cho} is similarly easy to pronounce and spell. I propose that it
be defined as ``A kind of cheese,'' so that we can really nail the new
triple entendre on the classic joke. {\it Chomaker} is someone who
makes that kind of cheese.

{\it Unders} was one of the most frequently occuring words towards the
top of many analyses. This word should be a colloquialism for
underwear, which would probably already be understood from context.

{\it Dise} is suggested by both the Markov model (as {\it dises}, {\it
  dising}) and backformation (as {\it dises}). I like thinking of it
as being the root of {\it paradise}, where {\it para--} means
something like ``along side of'' or ``resembling''. So {\it dise} is
the place you're really looking for when you get to paradise and
realize it's just a mediocre country club.

{\it Helafelo} is one hell of a fellow.

\medskip
{\bf Addendum.} During the preparation of this paper, the Scrallbe
game has converged on a culture where the words played are real-seeming,
with creative definitions. Examples: {\it frodeo} (``Gandalf is the
clown.'') {\it pridefax} (``An unproven treatment for telephone
anxiety.'') {\it eeeee} (``eeeee'') {\it orzigato} (``Move mr. roboto.
for great justice.'') {\it stovebed} (``Now you don't have to get out
from under the covers to make breakfast.'') {\it ovawiki} (``The free
egg cell that anyone can edit.'') {\it gaptave} (``Two discontinuous
musical intervals.'') {\it achoolane} (``Nostril (colloq.)'') {\it
  gplerious} (``Completely overcome by software licenses.) {\it
  bestcano} (``Some eruptions are better than others.'') Thanks to the
players for their contributions, especially Ben~Blum, Chrisamaphone,
Rob~Simmons, and Flammin~Fingers.

\section*{Appendix}

Here are the most likely words induced by the English Wikipedia, with $n=3$.
I have left off the probabilities; they can be reproduced by downloading
Wikipedia and running the software yourself, which only takes like 9 hours.

s
ther
w
en
t
c
d
f
m
b
ser
e
diff
u
sup
p
n
de
tal
othe
th
wikipedia
rd
con
id
r
ame
edia
cal
uk
wiki
und
als
st
l
km
wp
g
x
ext
j
des
td
ter
h
co
k
sout
don
o
cound
v
ver
wer
med
res
ind
la
em
re
ins
afd
ands
div
htm
infor
rom
wher
ple
mi
acces
ii
ent
unive
ff
refere
ger
bution
lish
ince
wikiped
auth
dist
oth
smally
rea
al
y
est
cle
fr
lation
tral
gov
nd
mily
isbn
cond
bel
befor
hould
ber
pers
inder
les
gree
mation
lar
chan
dia
ove
stary
compan
mon
val
san
cate
nothe
pdf
tes
ster
nort
pril
hist
sq
clast
ful
ment
q
aft
tr
nown
lign
del
z
ave
dify
stor
sity
artic
pring
rese
mas
li
ord
ca
thes
oldid
lin
es
ress
flage
blace
pland
mar
mes
conce
exter
wate
mp
jame
lity
ft
cology
spany
mic
ve
han
thist
spam
cand
sher
smal
subdiv
tem
jan
ture
inded
bothe
ared
cour
rect
thers
ope
mm
dom
der
mand
tt
dr
phy
cd
websity
stude
lor
bbc
ru
mer
flor
succes
ence
tely
aust
stan
clas
et
outh
pl
ints
vfd
fc
wikipedit
sus
forman
contry
au
edu
inding
el
lic
bord
mr
ston
whic
ide
hous
mich
auser
google
pt
le
doi
engle
ed
gen
userved
cols
num
nate
cer
withis
clude
shous
inted
wikipedian
thered
andex
chool
ning
attle
chael
sta
plation
ampion
crea
fontry
lege
prese
grough
iii
mader
augh
ll
ching
fb
furt
yearch
examp
octor
nove
furth
bein
tra
nover
texter
mont
sted
gener
quary
inclub
ander
sco
ast
gr
wome
ality
lon
hough
ano
exas
polid
sease
dec
sor
ga
nov
unty
shor
imdb
offic
partic
oved
forn
lan
fm
undex
rus
arted
alia
cong
vill
eason
gue
shough
cc
vil
tember
octory
jr
gove
writy
thand
anding
rev
colog
gover
edian
publist
mics
comple
syster
olding
coor
useum
spect
expan
puble
bate
tribut
oned
coibot
betwo
conter
cles
leason
fina
freen
eng
fa
que
fied
tre
hamp
guage
wered
nic
awar
yout
usic
cgi
andy
nrhp
clar
arting
bc
cated
rober
feb
ames
ven
jun
thould
defere
artics
sen
frand
cred
ada
cana
rection
modiff
sal
los
ret
ched
decial
collow
notalk
nl
yor
elete
sain
ance
cens
chand
apr
delect
dea
stant
bruary
commer
righ
ch
tor
peral
andia
arth
roup
founty
hor
scies
alth
pete
footnot
html
ath
tribs
ac
chas
eith
pa
tl
refor
bes
bor
cently
fonter
neer
tration
reat
hi
awa
chris
da
wikipedits
atter
pp
ents
dvd
arge
wan
sch
sr
fere
inds
norts
tha
nament
anot
oper
aspx
rence
website
minal
brity
dts
apring
goalso
alber
rown
graphy
anded
min
alian
ength
mility
abbr
talign
bec
com
authe
hite
pic
pation
jone
ords
demy
alt
wated
alife
totalk
lond
tage
ad
ana
evers
amg
gened
colo
engton
mina
lates
porth
fff
lifor
footbally
stry
shing
hase
lis
eletion
rol
mally
inton
ded
doesn
ny
mus
pro
du
pre
somes
dired
na
becamp
ire
inces
cologo
mong
swith
acts
aree
ang
els
noth
unic
mous
dest
ali
deat
smale
poing
dc
ission
iv
oct
posity
pred
poss
kore
anda
ja
ms
gard
coi
frome
afc
nhl
publice
mothe
jers
maded
qual
geory
roy
vid
pur
studing
ip
ign
fath
cally
coundex
col
abouth
twork
threen
img
ess
lishe
lable
reland
cing
chi
thern
dete
ar
ving
di
eur
wers
il
dio
hl
ando
seast
sation
orge
ble
sep
db
classion
cm
las
conver
evel
ing
popula
uns
polic
vs
frans
ker
ann
phich
ovember
alish
cher
therence
prock
ife
feate
uservice
indid
unded
powere
hs
phot
assion
von
dece
theight
proview
ama
prote
kg
birthe
specian
userve
se
nois
cfm
ma
len
ause
gle
jp
flagic
differe
counder
rance
swed
lee
tel
ont
sould
whics
artion
rans
ric
parly
overy
ves
sa
grea
ans
une
tary
ss
jul
ne
fami
dever
ange
hms
oright
dation
cription
prothe
univer
lat
tota
un
adming
aaa
ampan
perfor
athe
seased
pov
becaust
alson
thed
methe
aff
spand
inc
sis
stral
refered
endex
xfd
texamp
valign
sha
dists
fron
heade
lood
thest
unived
italk
brary
colled
ucfirst
ite
gan
ep
rary
oney
wikipedition
ra
ex
scord
cition
hout
clos
bon
lp
imple
acade
flagico
bost
isn
spection
samp
ral
tead
sant
roces
yorks
ories
bords
unition
che
dra
epison
eff
stal
abour
ach
earch
busic
reate
conves
ses
hims
mone
fran
carly
nated
lished
fra
pm
oh
att
delet
unior
reporth
daving
emple
tworld
noved
trand
ross
ie
vall
orld
vi
becauser
caust
dard
exand
feder
ches
yound
gence
bol
stribut
rement
gf
sugges
tity
forder
aug
systed
mathe
websited
abover
ltd
recember
colle
wils
mos
sman
lete
dow
eles
throup
ba
unt
expr
formany
df
ments
tect
pape
hool
exper
butions
hited
delection
deces
coung
gon
gers
stors
abc
partics
writion
furthe
rade
mult
bb
lism
afries
frence
bish
arence
tems
musion
colore
ethe
bute
vie
ia
hing
oute
hom
clain
nom
missue
hus
ns
chich
oxfor
contribut
vict
autom
boile
novers
aus
airst
jos
proble
werence
georgan
rel
eas
opedia
rs
ned
aut
iss
pg
ct
othis
indo
shi
dst
alf
ian
grounty
hile
mor
jor
grap
parth
elet
regory
thems
ell
septed
pc
url
gnf
unds
appy
studed
offere
gb
timent
sed
dary
eved
hally
deate
hr
taly
noming
duri
cented
thead
aliam
mored
pmid
hered
hong
recore
vious
wates
fathe
goved
squary
soment
mout
rela
eview
unives
shere
trate
betweek
gia
mory
cas
dal
fi
enge
stribs
colspan
vol
facted
amer
reser
loc
fination
deven
andid
leade
tand
protes
gar
dely
til
alled
sary
tro
alist
ng
cha
charly
ab
hel
begion
mana
sk
powed
ted
calign
wikipe
dar
nm
churce
mil
ren
dise
rever
sel
howere
nexter
commen
sonal
oly
subser
coibothe
shool
hal
froman
eu
waship
pr
rease
ph
rical
op
assed
bility
ording
conces
mal
stitle
iucn
sri
os
mond
lations
mance
artment
rigin
rt
brite
ffff
jsp
lb
dd
wikipeding
lant
sett
arter
te
yource
sh
contribs
footbal
zh
aution
acter
addit
govers
coln
useries
ract
thich
tain
inten
sec
aa
blo
janual
hon
nowing
letion
tition
pute
goldid
communite
wors
fontribut
areat
titute
rected
summent
stational
hu
counded
sp
eld
ples
yeare
nating
fing
foll
reque
fiel
pol
josed
atland
phile
manuary
civision
ok
feded
ult
dj
sas
alle
cg
buildid
kee
redia
ap
unk
ko
cr
inver
nomy
sund
toon
reg
aaaa
cath
dll
lc
ters
communive
bal
prope
refef
ania
mrs
hased
worder
pria
arry
centing
spon
ade
vand
dor
sourch
tooks
seph
capan
pbb
colong
sql
petion
shors
fift
prily
prial
brition
fl
seption
nz
fonto
cbs
fally
whill
losed
cluded
mations
monal
sland
pict
russion
profilm
coundo
reture
harly
soute
sc
rr
titution
therent
shouser
pager
outhe
quent
spons
fn
ited
proces
bable
atte
whicle
sile
si
rece
unitor
yan
grought
cos
pian
comput
trans
jource
arthe
tury
specia
artice
provid
raction
deleter
alo
fored
ti
eague
wiking
conth
ree
musly
ars
mf
ups
schood
rey
donal
sected
writed
freet
formate
cre
colution
opers
chen
bd
hp
sember
folled
pagest
smales
wen
socies
cs
engin
aften
chur
delp
bia
ce
nors
cource
ussion
fontribs
summan
arties
jon
dism
lang
sking
augus
theren
xs
seve
deball
er
uning
truction
nomic
creat
gian
acco
sv
pera
alls
rict
relete
rects
coord
stre
ences
aread
spane
meth
brea
ener
thernal
thire
whical
rounty
thu
cl
pola
una
thround
uservation
volved
hund
aga
cames
menter
froma
uset
publis
frey
libe
posite
northe
ska
appedia
recial
ro
fant
hought
mination
geo
presult
andon
occup
ala
nas
thists
ew
maring
secore
nee
dian
inders
inves
infore
hower
sume
scal
kans
indust
eding
ka
aux
brid
var
orded
gived
backgrough
hugh
ado
prive
eb
rading
joing
hown
euro
lim
kan
chus
alifor
wille
deced
conven
blogy
nbc
quall
coller
partion
folle
eleter
reven
reques
lition
humber
moder
backgroup
tribution
flages
lears
forch
reight
pault
evely
mayork
sition
feath
recont
guit
metion
hony
deview
nume
confere
fle
unitory
rican
ima
accore
deside
ris
pedia
lisher
acture
aland
userview
thate
polor
kar
nel
sents
pany
cluding
vard
bing
woul
havel
greer
thang
genry
effere
locall
desh
thors
empt
sult
quence
mir
blook
porthe
tran
rew
bording
shought
kely
neight
lam
stion
publishe
hors
wis
apan
nony
sourn
nage
orce
profest
jonal
fonth
younty
deta
pd
wa
lo
peries
flign
fource
ros
rfc
mely
mt
smalled
ge
retion
relect
vern
alid
aligh
userves
speer
willa
infl
undon
dels
aftern
gres
namedia
advan
distor
oria
subdiving
lx
presign
blocal
edway
def
scho
fic
counds
belf
sily
metry
cread
pi
novery
occes
cribut
holor
reces
inte
howed
cout
chis
ency
actory
lange
cf
nc
bornia
adven
revie
sames
newspan
shan
orial
userry
suff
eth
moto
showere
hunty
nucle
witz
ider
mune
flagicont
aire
shtm
fri
guary
rigion
mome
afted
heate
mo
formedia
oble
cnn
nea
ha
canage
borning
tol
navbox
ava
octors
md
frent
offical
wal
arent
anon
artish
cration
rell
dir
auding
ira
butional
labout
bott
southe
dence
sporth
formall
ps
intry
thamp
stube
unus
usering
ron
usert
conse
brote
lib
oces
bg
proad
tas
werent
chese
lyn
atta
pris
oile
drage
unre
whenry
ement
stada
chara
raphy
tection
rica
reletion
foothe
titler
lassion
areen
theim
conship
formand
ution
unio
ided
guid
riging
brited
buch
septem
eleted
conds
preser
ta
ort
feld
ine
actional
alize
tex
fer
aused
engly
eque
sevel
atted
smalle
thome
alty
reath
gation
prefere
hd
nr
peration
covember
govember
livision
fren
dq
aren
deve
va
ffcc
jo
prian
afl
gion
medy
stategory
nomich
tured
mel
ene
appa
licy
linal
rought
areate
bethe
othey
eral
opport
ara
kw
whild
cance
communited
varing
brothe
pia
mu
sched
socian
poin
vis
obs
squal
paking
sma
convers
noing
maken
cathe
ni
solor
alry
flagicons
aaaaa
weren
artical
mtv
flagion
chall
alm
upons
dister
searly
sur
towned
oring
ests
avg
whis
publicy
ec
thange
gp
ced
pes
whick
figh
peted
fed
sween
discore
sil
ds
sournal
tay
dier
kim
adver
reak
mote
wouldn
paign
inal
medit
pointo
cata
sper
pts
idw
mlb
guis
cational
ul
wasn
septer
aird
throm
fe
feated
collo
itary
uni
uple
distory
disa
regist
vere
effor
whican
ober
bettle
anning
cution
speciate
palign
ai
cit
moview
flagicon
af
covery
govery
lina
reast
creen
texand
exten
vic
